---
title: "p8105_homework2_qs2200"
author: "Qi Shao"
date: "10/2/2018"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
```

# Problem 1
```{r problem 1.1, message = FALSE}
transit_data = 
  read_csv(file = "./data/NYC_Transit_Subway_Entrance_And_Exit_Data.csv") %>%
  janitor::clean_names() %>%
  select(line, station_name, station_latitude, station_longitude, route1:route11, entry, vending, entrance_type, ada) %>%
  mutate(entry = recode(entry, `YES` = "TRUE", `NO` = "FALSE")) %>%
  mutate(entry = as.logical(entry))
```

**1. Describe the dataset.**

This dataset `transit_data` contains `r ncol(transit_data)` variables, they are `r names(transit_data)`.
At first I import the dataset, and clean it's name using the function`janitor::clean_names`, and select required columns, change the variable type of the entry variable.

The result dataset is `r nrow(transit_data)` rows by `r ncol(transit_data)`columns.

These data are still untidy, the route number and route name variables are not clear for people to read.

